\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-29 paper/eprv.tex
tweak
estimators section done

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\foreign}[1]{\textsl{#1}}

@@

Earth-like planets induce $0.1\,\mps$-level signals in their host
stars!
Substantial hardware, software, and systems-engineering effort has
been put into the challenges of making measurements at this level of
precision (CITE some reviews).
It appears that contemporary spectrographs are stable at the
$0.05\,\mps$ level (CITE THINGS), and that the information content in
the data---which is set by the spectral features, the spectrograph
resolution, the wavelength range, and the observational
signal-to-noise (CITE THINGS)---is sufficient.
And yet, the best published \RV\ data sets show empirical scatter
(rms variations around best-fit kinematic models, for example) at the
$1\,\mps$ level (for example, CITE THINGS).
We hear rumors of various projects delivering empirical scatters for
the best stars at the $0.2$ to $0.5\,\mps$ level
(J.~Brewer \& D.~Fischer, private communication; F.~Pepe, private communication)
but they aren't yet published.
One of the motivating questions for this \documentname\ is: Is it possible that
the data-analysis methodologies currently in use are contributing to this
empirical variance?
That is, are we getting the precision we should be, given the data
quality?
This is a question in information theory and inference.

@@

Ultra-stabilized spectrographs like \HARPS\ \todo{(define \& cite)}
predominantly utilize a cross-correlation method with a custom-built
list of spectral lines (see e.g. Queloz1995, Baranne1996).
A lesser-used alternative is cross-correlation or maximum-likelihood
fitting using a template spectrum generated from the data \todo{(Buchhave,
Anglada-Escude)}.
This often involves masking or downweighting of the most
telluric-contaminated spectral regions.
As an alternative, gas-cell-calibrated spectrographs like
\HIRES\ \todo{(CITE)} commonly adopt more of a forward-modeling approach.
In this framework, the instrumental line spread function, the stellar
RV, and other parameters are optimized by modeling each observation as
a combination of shifted and instrument-convolved template spectra for
the star and gas cell (CITE).
Here we focus on the ultra-stabilized spectrograph hardware, but consider
a few different data-analysis approaches.
Most of what we do here could be generalized to data generated by
gas-cell hardware; we will return to this point in the discussion.

@@

The most optimistic assumptions we can possibly make are the following.
\begin{itemize}
\item The spectrograph is perfectly calibrated in a wavelength sense.
\item The spectrograph is consistently and repeatably calibrated in a
  flux sense. That is, the spectrum does not need to be perfectly
  continuum-normalized or perfectly flux-normalized, but it is
  calibrated near-perfectly \emph{consistently} across epochs (exposures).
  We will break this assumption in our experiments, below.
\item There are no residual telluric absorptions nor any residual sky
  emission in the spectra. That is, the sky is near-perfectly calibrated
  and removed.
  We will also break this assumption in our experiments, below.
\item The \emph{true} spectrum (that is, the latent spectrum that
  would be observed if the data were far, far better) of the star is
  known at better accuracy and precision than the main noise sources.
  We will break this assumption too.
  The whole point of this paper is to ask whether we can create a
  good-enough proxy for the true spectrum.
\item There is no time dependence (no epoch-to-epoch variations) in the
  stellar spectrum.
\item All noise sources contributing to the spectral data---which
  include at a minimum photon noise, read noise, residual telluric
  issues, residual wavelength-calibration issues, and residual stellar
  spectral variability---are, when summed together, indistinguishable
  from being zero-mean, Gaussian, and additive.
\item The complete variance tensor of the total noise on the spectrum is known, and
  known correctly. That is, the variance of the noise at every pixel
  is known, as is the covariance between nearby pixels, and in the
  same \emph{true} sense that the true spectrum of the star is known.
\end{itemize}
It is worthy of note that every formula (that we know) in the
literature for maximum \RV\ precision (\todo{cite Butler, Bouchy,
  Figueira, Lovis}) makes all of these same assumptions,
plus additional \emph{even more restrictive assumptions}.
Under these disturbingly unrealistic assumptions, the \CRLB\ becomes
\begin{equation}\label{eq:crlb}
\frac{1}{\sigma_v^2} \leq \left[\frac{\dd f(v)}{\dd v}\right]\T\cdot C^{-1}\cdot\left[\frac{\dd f(v)}{\dd v}\right]
\end{equation}
where the derivatives are of the true spectrum $f(v)$ with respect to
radial velocity $v$ (which can, in turn, be thought of as the derivative of a Doppler
operator with respect to velocity acting on the true spectrum; CITE WOBBLE), the
derivatives are column vectors, and $C^{-1}$ is the inverse of the covariance matrix
describing the true variance and covariances of the noise process.

Formulae (bounds) related to (\ref{eq:crlb}) have appeared previously
in the literature, although in somewhat more complicated forms.
Butler (\todo{cite}) shows a similar expression, but makes the additional
assumption that every pixel is independent; that is, that there is no
covariance between nearby pixels from, say, extraction or continuum normalization.
Bouchy (\todo{cite}) shows an expression that assumes that the pixels
are independent and that the noise is dominated by a combination of photon
and read noise. 
That work also replaces the model spectrum with a set of optimal
weights for cross-correlation, which amounts to very much the same thing,
as we will discuss below.
Figueira (\todo{cite}) and \todo{others (cite)} show a per-line
bound, based on assumptions similar to those of Bouchy but with the additional assumption that
each line is well approximated by a Gaussian (squared exponential) in shape.
These literature bounds are all extremely similar, and similar to (\ref{eq:crlb});
nothing here is controversial.
We will come back to the scaling of uncertainty with various
Gaussian line parameters in \sectionname~\ref{s:singleline}.

@@

\CRLB-saturating estimators are (or are equivalent to)
maximum-likelihood estimators.
When the likelihood is Gaussian, the log-likelihood
is a sum of a quadratic chi-squared-like term and a log-determinant term
\begin{equation}
\ln L = -\frac{1}{2}\,[y - f(v)]\T\cdot C^{-1}\cdot [y - f(v)] - \frac{1}{2}\,\ln||2\pi\,C|| \quad ,
\label{eq:lf}
\end{equation}
where $y$ is a column vector of the data, $f(v)$ is the model spectrum,
which depends on the \RV\ $v$,
and $C$ is the covariance matrix describing the noise variance.
In the case of independent pixel noise the chi-squared term just becomes an
inverse-variance weighted sum of squared residuals (chi-squared).
The maximum-likelihood estimator for $v$ is the value of $v$ which maximizes
the log-likelihood.
Since only the chi-squared term depends on $v$, maximizing the likelihood
means minimizing chi-squared.

Most methods for radial-velocity estimation aren't explicitly maximizing
any likelihood.
Instead, they involve some kind of
cross-correlation of the data with a template.
This might be surprising, since (as we noted above) bound-saturating
estimators will be maximum-likelihood estimators.
However, under simple assumptions, cross-correlation optima are
also maximum-likelihood optima. The argument is as follows:
If we expand the quadratic form (chi-squared term) in the
likelihood in equation~(\ref{eq:lf}), it becomes
\begin{equation}
 {}-\frac{1}{2}\,y\T\cdot C^{-1}\cdot y
               + y\T\cdot C^{-1}\cdot f(v)
-\frac{1}{2}\,f(v)\T\cdot C^{-1}\cdot f(v) \quad.
\end{equation}
That is, the chi-squared term factors into a term that is the square
of the data $y$, a term that is the square of the model $f(v)$,
and a term that is a scalar product or projection or
cross correlation of data with model.
As long as the amplitude of $f(v)$ doesn't depend strongly on velocity $v$,
and the $C$ tensor is ``smooth'' in certain respects, the dependence of this
chi-squared term on velocity will be dominated by the
cross-correlation.
For this reason, we can use a variant of cross-correlation
optimization as a radial-velocity estimator, or, in other words, the
\RV\ $v$ that optimizes $y\T\cdot C^{-1}\cdot f(v)$ will also (nearly)
optimize the likelihood.

In actually performing this cross-correlation optimization,
investigators make some non-trivial choices.
The first is whether or not to use the inverse variance tensor $C$.
Many codes do not make any use of the uncertainty estimates at all in
the calculation of the cross correlation.
Not using the uncertainties (treating $C$ as the identity) is
equivalent to assuming that the pixel uncertainties don't vary much
from pixel to pixel across the spectrum.
If the cross correlation is optimized with $C$ set to the identity,
the optimum of that doesn't strictly optimize the likelihood function;
the differences depdends on the variations in the uncertainties.
Another choice is how finely to sample in radial velocity $v$, or how
to perform the optimization.
If the $v$ spacing is coarse (but not too coarse!), quadratic
interpolation can be used to find the optimum at high precision.
The velocity spacing need only be smaller than something like half the
spectral velocity resolution ($c\,\Delta\lambda / \lambda$).
This problem is similar to stellar centroiding methods in use in
imaging surveys (CITE VAKILI).
Another choice faced by an investigator is what to do at the ends or
edges of the spectra or spectral segments used for the
cross-correlation.
If the edges are treated naively, it is possible to introduce unintended
dependencies that invalidate the requirement that the model-times-model term
(the $f(v)\T\cdot C^{-1}\cdot f(v)$ term) not depend on \RV\ $v$.

HOGG ...In detail, in the experiments that follow, the
cross-correlation we will optimize has the following properties...

The maximum-likelihood and cross-correlation methods only give
bound-saturating \RV\ estimates when the spectral model $f(v)$
respresents something similar to the true expecation of the spectrum
at velocity $v$.
And yet there is a paradox, because many world-class \RV\ pipelines
(like for instance HOGG CITE) perform cross-correlation with a
\emph{binary mask}.
This is not a good representation of the spectral expectation! So why
do these methods work to deliver high quality \RV\ estimates.
The answer is that the codes that cross-correlate with a binary mask
subsequently fit that cross-correlation with a Gaussian function.
It turns out that the operation ``cross-correlate the data with a
binary mask, followed by fitting a Gaussian to the cross-correlation
function'' is mathematically equivalent to ``smooth the binary mask
with a Gaussian, and then cross-correlate with the data''.
That is, when a pipeline cross-correlates with a binary mask and then
fits that cross-correlation function with a Gaussian, it is equivalent
to smoothing the binary mask with a best-fitting Gaussian function to
make a smooth, realistic $f(v)$ and then cross-correlating with that
realistic $f(v)$.
The fitting gives the flexibility to match the spectral resolution of
the template to the spectral resolution of the data, in the
approximation that the resolution is close to constant over the
spectral range in velocity units.
So in all cases of bound-saturating \RV\ measurements, the
\RV\ estimation is effectively a good approximation to
maximum-likelihood with a good spectral template.

\todo{HOGG: SYNTACTICAL REFERENCE}

A variety of choices exist for the cross-correlation template $f$. A few possibilities include:
\begin{itemize}
\item a ``binary'' mask, or a spectrum of zero value with non-zero peaks at the expected rest-frame wavelengths of the spectral lines of interest. A cross-correlation between this mask and the observed spectrum will effectively compute the average line profile with its minimum corresponding to the best-fit RV. This method has the benefit of trivially excluding telluric-contaminated or otherwise unreliable regions of the spectrum by deleting them from the mask. A desired relative weighting of lines can be incorporated by setting the non-zero mask values to different amplitudes at different lines (cite Pepe). This method is currently used by the \HARPS\ pipeline (cite).
\item synthetic spectrum (i.e. a slightly wrong model prediction, since the stellar model will never be a perfect reproduction of the star in question): sub-tweet: some surveys cross-correlate with a single (same) template for every single star, which is extremely wrong. you can be more right by using a spectral-type-specific template.
\item data-driven template spectrum: some surveys (HIRES) use a single observation as a template. combining information from many visits is better because the combined SNR is amazing.
\end{itemize}

One final implementation detail is the following:
When we optimize the cross-correlation function, we don't run an optimizer;
we perform brute-force search on a linear velocity grid.
This grid, however, does not need to be fine.
We use a coarse grid (\todo{give grid spacing here}), which does not
over-resolve the velocity peak at the optimum.
We then take the highest value on the grid and the values on either
side, fit a parabola through those three values, and take as the optimal
velocity the peak of that parabola.
That is, we obtain sub-grid velocity resolution by means of a quadratic
interpolation at the peak on the finite grid.
\todo{Do we need to demonstrate this with a toy figure?}

\begin{figure}
\centering
% \includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window corresponds to the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

@@

>>>>

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}
\renewcommand{\paragraph}[1]{\bigskip\par\noindent\textsl{#1} ---}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\CITE}{\todo{CITE}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\foreign}[1]{\textsl{#1}}

@@

Earth-like planets induce $0.1\,\mps$-level signals in their host
stars!
Substantial hardware, software, and systems-engineering effort has
been put into the challenges of making measurements at this level of
precision (\CITE some reviews).
It appears that contemporary spectrographs are stable at the
$0.05\,\mps$ level (\CITE THINGS), and that the information content in
the data---which is set by the spectral features, the spectrograph
resolution, the wavelength range, and the observational
signal-to-noise (\CITE THINGS)---is sufficient.
And yet, the best published \RV\ data sets show empirical scatter
(rms variations around best-fit kinematic models, for example) at the
$1\,\mps$ level (for example, \CITE THINGS).
We hear rumors of various projects delivering empirical scatters for
the best stars at the $0.2$ to $0.5\,\mps$ level
(J.~Brewer \& D.~Fischer, private communication; F.~Pepe, private communication)
but they aren't yet published.
One of the motivating questions for this \documentname\ is: Is it possible that
the data-analysis methodologies currently in use are contributing to this
empirical variance?
That is, are we getting the precision we should be, given the data
quality?
This is a question in information theory and inference.

@@

Ultra-stabilized spectrographs like \HARPS\ \todo{(define \& \CITE)}
predominantly utilize a cross-correlation method with a custom-built
list of spectral lines (see e.g. Queloz1995, Baranne1996).
A lesser-used alternative is cross-correlation or maximum-likelihood
fitting using a template spectrum generated from the data \todo{(Buchhave,
Anglada-Escude)}.
This often involves masking or downweighting of the most
telluric-contaminated spectral regions.
As an alternative, gas-cell-calibrated spectrographs like
\HIRES\ \todo{(CITE)} commonly adopt more of a forward-modeling approach.
In this framework, the instrumental line spread function, the stellar
RV, and other parameters are optimized by modeling each observation as
a combination of shifted and instrument-convolved template spectra for
the star and gas cell (\CITE).
Here we focus on the ultra-stabilized spectrograph hardware, but consider
a few different data-analysis approaches.
Most of what we do here could be generalized to data generated by
gas-cell hardware; we will return to this point in the discussion.

@@

The most optimistic assumptions we can possibly make are the following.
\begin{itemize}
\item The spectrograph is perfectly calibrated in a wavelength sense.
\item The spectrograph is consistently and repeatably calibrated in a
  flux sense. That is, the spectrum does not need to be perfectly
  continuum-normalized or perfectly flux-normalized, but it is
  calibrated near-perfectly \emph{consistently} across epochs (exposures).
  We will break this assumption in our experiments, below.
\item There are no residual telluric absorptions nor any residual sky
  emission in the spectra. That is, the sky is near-perfectly calibrated
  and removed.
  We will also break this assumption in our experiments, below.
\item The \emph{true} spectrum (that is, the latent spectrum that
  would be observed if the data were far, far better) of the star is
  known at better accuracy and precision than the main noise sources.
  We will break this assumption too.
  The whole point of this paper is to ask whether we can create a
  good-enough proxy for the true spectrum.
\item There is no time dependence (no epoch-to-epoch variations) in the
  stellar spectrum.
\item All noise sources contributing to the spectral data---which
  include at a minimum photon noise, read noise, residual telluric
  issues, residual wavelength-calibration issues, and residual stellar
  spectral variability---are, when summed together, indistinguishable
  from being zero-mean, Gaussian, and additive.
\item The complete variance tensor of the total noise on the spectrum is known, and
  known correctly. That is, the variance of the noise at every pixel
  is known, as is the covariance between nearby pixels, and in the
  same \emph{true} sense that the true spectrum of the star is known.
\end{itemize}
It is worthy of note that every formula (that we know) in the
literature for maximum \RV\ precision (\todo{cite Butler, Bouchy,
  Figueira, Lovis}) makes all of these same assumptions,
plus additional \emph{even more restrictive assumptions}.
Under these disturbingly unrealistic assumptions, the \CRLB\ becomes
\begin{equation}\label{eq:crlb}
\frac{1}{\sigma_v^2} \leq \left[\frac{\dd f(v)}{\dd v}\right]\T\cdot C^{-1}\cdot\left[\frac{\dd f(v)}{\dd v}\right]
\end{equation}
where the derivatives are of the true spectrum $f(v)$ with respect to
radial velocity $v$ (which can, in turn, be thought of as the derivative of a Doppler
operator with respect to velocity acting on the true spectrum; \CITE WOBBLE), the
derivatives are column vectors, and $C^{-1}$ is the inverse of the covariance matrix
describing the true variance and covariances of the noise process.

Formulae (bounds) related to (\ref{eq:crlb}) have appeared previously
in the literature, although in somewhat more complicated forms.
Butler (\todo{cite}) shows a similar expression, but makes the additional
assumption that every pixel is independent; that is, that there is no
covariance between nearby pixels from, say, extraction or continuum normalization.
Bouchy (\todo{cite}) shows an expression that assumes that the pixels
are independent and that the noise is dominated by a combination of photon
and read noise. 
That work also replaces the model spectrum with a set of optimal
weights for cross-correlation, which amounts to very much the same thing,
as we will discuss below.
Figueira (\todo{cite}) and \todo{others (\CITE)} show a per-line
bound, based on assumptions similar to those of Bouchy but with the additional assumption that
each line is well approximated by a Gaussian (squared exponential) in shape.
These literature bounds are all extremely similar, and similar to (\ref{eq:crlb});
nothing here is controversial.
We will come back to the scaling of uncertainty with various
Gaussian line parameters in \sectionname~\ref{s:singleline}.

@@

There are three dominant methods for the estimation of a radial veloctity,
given spectral data.

\paragraph{Maximum-likelihood estimator}
\CRLB-saturating estimators are (or are equivalent to)
maximum-likelihood estimators.
When the likelihood is Gaussian, the log-likelihood
is a sum of a quadratic chi-squared-like term and a log-determinant term
\begin{equation}
\ln L = -\frac{1}{2}\,[y - f(v)]\T\cdot C^{-1}\cdot [y - f(v)] - \frac{1}{2}\,\ln||2\pi\,C||
\quad ,
\label{eq:lf}
\end{equation}
where $y$ is a column vector of the data, $f(v)$ is the model spectrum,
which depends on the \RV\ $v$,
and $C$ is the covariance matrix describing the noise variance.
In the case of independent pixel noise the chi-squared term just becomes an
inverse-variance weighted sum of squared residuals (chi-squared).
The maximum-likelihood estimator for $v$ is the value of $v$ which maximizes
the log-likelihood.
Since only the chi-squared term depends on $v$, maximizing the likelihood
means minimizing chi-squared.
Optimization is straightforward; it is one-dimensional optimization
(given the template spectrum $f(v)$, and derivatives with respect to
velocity are easy to take:
\begin{equation}
\frac{\dd\ln L}{\dd v} = [\frac{\dd f(v)}{\dd v}]\T\cdot C^{-1}\cdot [y - f(v)]
\quad .
\label{eq:dldv}
\end{equation}

\paragraph{Cross correlation with a template}
Most methods for radial-velocity estimation aren't explicitly maximizing
any likelihood.
Instead, they involve some kind of
cross-correlation of the data with a template.
This might be surprising, since (as we noted above) bound-saturating
estimators will be maximum-likelihood estimators.
However, under simple assumptions, cross-correlation optima are
also maximum-likelihood optima. The argument is as follows:
If we expand the quadratic form (chi-squared term) in the
likelihood in equation~(\ref{eq:lf}), it becomes
\begin{equation}
 {}-\frac{1}{2}\,y\T\cdot C^{-1}\cdot y
            + f(v)\T\cdot C^{-1}\cdot y
-\frac{1}{2}\,f(v)\T\cdot C^{-1}\cdot f(v) \quad.
\end{equation}
That is, the chi-squared term factors into a term that is the square
of the data $y$, a term that is the square of the model $f(v)$,
and a term that is a scalar product or projection or
cross correlation of data with model.
As long as the amplitude of $f(v)$ doesn't depend strongly on velocity $v$,
and the $C$ tensor is ``smooth'' in certain respects, the dependence of this
chi-squared term on velocity will be dominated by the
cross-correlation.
For this reason, we can use a variant of cross-correlation
optimization as a radial-velocity estimator, or, in other words, the
\RV\ $v$ that optimizes $f(v)\T\cdot C^{-1}\cdot y$ will also (nearly)
optimize the likelihood.

Another argument is as follows:
As long as the derivative $\dd f(v)/\dd v$ is close to orthogonal
(given the $C^{-1}$ metric) to the template $f(v)$, the derivative of
the log likelihood given in equation~(\ref{eq:dldv}) is equal to the
derivative of the cross-correlation $f(v)\T\cdot C^{-1}\cdot y$.
Therefore, whatever optimizes the likelihood will (nearly) optimize
the cross-correlation.

In actually performing this cross-correlation optimization,
investigators make some non-trivial choices.
The first is whether or not to use the inverse variance tensor $C$.
Many codes do not make any use of the uncertainty estimates at all in
the calculation of the cross correlation.
Not using the uncertainties (treating $C$ as the identity) is
equivalent to assuming that the pixel uncertainties don't vary much
from pixel to pixel across the spectrum.
If the cross correlation is optimized with $C$ set to the identity,
the optimum of that doesn't strictly optimize the likelihood function;
the differences depdends on the variations in the uncertainties.
Another choice is how finely to sample in radial velocity $v$, or how
to perform the optimization.
If the $v$ spacing is coarse (but not too coarse!), quadratic
interpolation can be used to find the optimum at high precision.
The velocity spacing need only be smaller than something like half the
spectral velocity resolution ($c\,\Delta\lambda / \lambda$).
This problem is similar to stellar centroiding methods in use in
imaging surveys (\CITE VAKILI).
Another choice faced by an investigator is what to do at the ends or
edges of the spectra or spectral segments used for the
cross-correlation.
If the edges are treated naively, it is possible to introduce unintended
dependencies that invalidate the requirement that the model-times-model term
(the $f(v)\T\cdot C^{-1}\cdot f(v)$ term) not depend on \RV\ $v$.

\todo{HOGG ...In detail, in the experiments that follow, the
cross-correlation we will optimize has the following properties...}

\paragraph{Cross correlation with a binary mask}
The maximum-likelihood and cross-correlation methods only give
bound-saturating \RV\ estimates when the spectral model $f(v)$
respresents something similar to the true expecation of the spectrum
at velocity $v$.
And yet there is a paradox, because many world-class \RV\ pipelines
(like for instance \\CITE) perform cross-correlation with a
\emph{binary mask}.
This is not a good representation of the spectral expectation! So why
do these methods deliver high quality \RV\ estimates?
The answer is that the codes that cross-correlate with a binary mask
subsequently fit that cross-correlation with a Gaussian function.
It turns out that the operation ``cross-correlate the data with a
binary mask, followed by fitting a Gaussian to the cross-correlation
function'' is mathematically equivalent to ``smooth the binary mask
with a Gaussian, and then cross-correlate with the data''.
That is, when a pipeline cross-correlates with a binary mask and then
fits that cross-correlation function with a Gaussian, it is equivalent
to smoothing the binary mask with a best-fitting Gaussian function to
make a smooth, realistic $f(v)$ and then cross-correlating with that
realistic $f(v)$.
The fitting gives the flexibility to match the spectral resolution of
the template to the spectral resolution of the data, in the
approximation that the resolution is close to constant over the
spectral range in velocity units.
So in all cases of bound-saturating \RV\ measurements, the
\RV\ estimation is effectively a good approximation to
maximum-likelihood with a good spectral template.

\paragraph{Choice of template}
A variety of choices exist for the cross-correlation template
$f(v)$. A few possibilities include:
\begin{itemize}
\item \emph{A theoretically produced synthetic spectrum:}
  This will be a slightly wrong model prediction,
  since no stellar model will produce perfect reproduction of the
  spectral expectation for the star in question.
  The chosen template should be matched as closely as possible however
  to the target star. Some surveys cross correlate with one universal
  template for all stars; this will lead to increases in both bias and
  variance relative to the \CRLB.
\item \emph{A binary mask:}
  This is a or a spectrum of zero values with non-zero top-hats at the
  expected rest-frame wavelengths of the spectral lines of interest.
  A cross-correlation between this mask and the observed spectrum will
  effectively compute the average line profile with its minimum
  corresponding to the best-fit RV.
  As we note above, fitting that mean line profile with a Gaussian
  before identifying the \RV\ estimate is equivalent to smoothing the
  mask with a Gaussian and then using it as the stellar template in a
  straightforward cross correlation.
  The binary-mask method has the benefit of exactly zeroing out
  telluric-contaminated or otherwise unreliable regions of the
  spectrum (by deleting them from the mask).
  A desired relative weighting of lines can be incorporated by setting
  the non-zero mask values to different amplitudes at different lines
  (\CITE Pepe). This method is currently used by the \HARPS\ pipeline
  (\CITE), and an example is shown in \figurename~\ref{fig:binarymask}.
\item \emph{A data-driven estimate of the template spectrum:}
  Some surveys (for example, \HIRES, \CITE) use a single observation as a
  template.
  Combining information from many visits is better because the
  combined SNR will be higher.
  In what follows, we show that with sufficient epochs, a data-driven
  template is accurate enough to saturate the \CRLB.
\end{itemize}
\begin{figure}[htp]
\centering
% \includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window corresponds to the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

@@

\todo{HOGG SYNTACTICAL}
